Wikipedia Text Mining and Entropy Analysis

### 2018-10-29 childes/childes_ce_and_mi.Rmd
Reorganized files, deleted redundant and obsfucating code

```{r presentation}

@@

all_conditional_entropy <- function(df) {
  max_len <- max(df$word_order)
  perms <- permutations(max_len, 2, 1:max_len, repeats.allowed = F) 
  combs <-  setNames(split(perms, seq(nrow(perms))), rownames(perms))

  map(combs, ~conditional_entropy(df, .x[1], .x[2])) %>%
    bind_rows()

conditional_entropy <- function(df, X, Y) { #Y is conditioning variable

@@

@@

  ce <- map(2:6, ~get_counts(role, .x, utterances)) %>% 
    map(~filter(.,word_order <= length)) %>%
    map(all_conditional_entropy) %>%
    bind_rows()

@@

```{r work_progress}

@@

wagner_ce_children <- get_ce(wagner_utterances, "Target_Child")
wagner_ce_adults <- get_ce(wagner_utterances, "not child")

ggplot(wagner_ce_children, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (Wagner children)")

ggplot(wagner_ce_adults, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (Wagner adults)")

okayama_mi_children <- get_mi(okayama_utterances, "Target_Child")
okayama_mi_adults <- get_mi(okayama_utterances, "not child")

ggplot(okayama_mi_children, aes(x = pos1, y = mi, color = as.factor(pos2))) + 
  facet_wrap(~length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Mutual information vs. conditioned position (Okayama children)")

ggplot(okayama_mi_adults, aes(x = pos1, y = mi, color = as.factor(pos2))) + 
  facet_wrap(~length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Mutual information vs. conditioned position (Okayama adults)")

okayama_ce_children <- get_ce(okayama_utterances, "Target_Child")
okayama_ce_adults <- get_ce(okayama_utterances, "not child")

ggplot(okayama_ce_children, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (Okayama children)")

ggplot(okayama_ce_adults, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (Okayama adults)")

miipro_mi_children <- get_mi(miipro_utterances, "Target_Child")
miipro_mi_adults <- get_mi(miipro_utterances, "not child")

ggplot(miipro_mi_children, aes(x = pos1, y = mi, color = as.factor(pos2))) + 
  facet_wrap(~length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Mutual information vs. conditioned position (Miipro children)")

ggplot(miipro_mi_adults, aes(x = pos1, y = mi, color = as.factor(pos2))) + 
  facet_wrap(~length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Mutual information vs. conditioned position (Miipro adults)")

miipro_ce_children <- get_ce(miipro_utterances, "Target_Child")
miipro_ce_adults <- get_ce(miipro_utterances, "not child")

ggplot(miipro_ce_children, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (Miipro children)")

ggplot(miipro_ce_adults, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (Miipro adults)")

zhou_mi_children <- get_mi(zhou_dinner, "Target_Child")
zhou_mi_adults <- get_mi(zhou_dinner, "not child")

ggplot(zhou_mi_children, aes(x = pos1, y = mi, color = as.factor(pos2))) + 
  facet_wrap(~length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Mutual information vs. conditioned position (Zhou children)")

ggplot(zhou_mi_adults, aes(x = pos1, y = mi, color = as.factor(pos2))) + 
  facet_wrap(~length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Mutual information vs. conditioned position (Zhou adults)")

zhou_ce_children <- get_ce(zhou_dinner, "Target_Child")
zhou_ce_adults <- get_ce(zhou_dinner, "not child")

ggplot(zhou_ce_children, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (Zhou children)")

ggplot(zhou_ce_adults, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (Zhou adults)")

leveille_ce_children <- get_ce(leveille_utterances, "Target_Child")
leveille_ce_adults <- get_ce(leveille_utterances, "not child")

ggplot(leveille_ce_children, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (Leveille children)")

ggplot(leveille_ce_adults, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable (Leveille adults)")
```

>>>>

```{r ce_and_mi_functions}

@@

position_ce <- function(df, X, Y) { #Y is conditioning variable

@@

all_pairwise_ce <- function(df) {
  max_len <- max(df$word_order)
  perms <- permutations(max_len, 2, 1:max_len, repeats.allowed = F) 
  combs <-  setNames(split(perms, seq(nrow(perms))), rownames(perms))

  map(combs, ~position_ce(df, .x[1], .x[2])) %>%
    bind_rows()

@@

  ce <- map(2:6, ~get_counts(role, .x, utterances)) %>% 
    map(~filter(.,word_order <= length)) %>%
    map(all_pairwise_ce) %>%
    bind_rows()

@@

```{r example_run}

@@

### 2018-10-29 childes/childes_entropy.Rmd
Reorganized files, deleted redundant and obsfucating code

  tokens <- lengths %>% 
    filter(length == target_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    summarise(n = n()) 
}

@@

  tokens <- lengths %>% 
    filter(length == target_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    filter(word_order <= length) %>% 
    summarise(n = n()) 
}

@@

  rbind(start_slopes, second_slopes, mid_slopes, penult_slopes, end_slopes)
}

```{r log_lengths}
tokens <- extract_tokens("not child", 6, 30, prov_utterances)

@@

extract_tokens <- function(role, min_length, max_length, utterances) {

  if (role == "child") {
    lengths <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(stem, " +") +1)

} else {
    lengths <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
     mutate(length = str_count(stem, " +") +1)
}

shiro_slopes <- map(6:10, ~get_slopes("child", .x, shiro_utterances, "gloss"))

shiro_slopes <- get_slopes("child", 6, shiro_utterances, "gloss") #what we would expect
shiro_slopes <- get_slopes("not child", 6, shiro_utterances, "gloss")
wagner_slopes <- get_slopes("child", 6, wagner_utterances, "gloss")
okayama_slopes <- get_slopes("child", 6, okayama_utterances, "gloss")
zhou_slopes <- get_slopes("child", 6, zhou_utterances, "stem")

start_time <- Sys.time()
samples <- replicate(1000, start_slope(tokens))  %>%
  as_data_frame()
end_time <- Sys.time()

end_time - start_time

start_slopes <- samples %>%
  summarise(mean = mean(value), ci_upper = quantile(value, .975), 
            ci_lower = quantile(value, .025))

```{r slope_analysis}

new_get_tokens <- function(role, min_length, max_length, utterances) {

  if (role == "child") {
        lengths <- utterances %>%
            filter(speaker_role != "Target_Child") %>%
            mutate(length = str_count(gloss, " ") + 1)

  } else {

        lengths <- utterances %>%
            filter(speaker_role != "Target_Child") %>%
            mutate(length = str_count(gloss, " ") + 1)
  }

  sub_tokens <- lengths %>% 
     mutate(gloss = str_trim(gloss)) %>%
     mutate(length = str_count(gloss, " +") +1) %>%
     filter(length >= min_length) %>%
     filter(length <= max_length) %>%
     mutate(utterance_id = 1:n()) %>%
     unnest_tokens(word, gloss, token = stringr::str_split, pattern = " +") %>%
     group_by(utterance_id) %>%
     mutate(word_order = 1:n()) %>%
     group_by(length, word_order, word) %>%
     filter(word_order <= length) %>% 
     summarise(n = n()) 
}

tkns <- new_get_tokens("child", 6, 20, prov_utterances)

new_tkns <- tkns %>% 
    filter(word_order %in% c(1,2)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2"), n = n()) %>%
    spread(word_order, entropy) %>%
    group_by(length) %>%
    mutate(diff = `2` - `1`) %>%
  ggplot(aes(x = length, y = diff)) +
  geom_point(aes(size = n)) +
  geom_smooth(se = F) +
  scale_x_log10()

min_length <- 6
max_length <- 20

lengths <- prov_utterances %>%
       filter(speaker_role != "Target_Child") %>%
       mutate(length = str_count(gloss, " ") + 1)

sub_tokens <- lengths %>% 
     mutate(gloss = str_trim(gloss)) %>%
     mutate(length = str_count(gloss, " +") +1) %>%
     filter(length >= min_length) %>%
     filter(length <= max_length) %>%
     mutate(utterance_id = 1:n())

sub_tokens %>%
     unnest_tokens(word, gloss, token = stringr::str_split, pattern = " +") %>%
     group_by(utterance_id) %>%
     mutate(word_order = 1:n()) %>%
     group_by(utterance_id) %>%
     summarise(n = n()) %>%
     # filter(n != 6) %>%
     left_join(sub_tokens) %>%
     select(gloss, n, length) %>%
     View()

Compute Providence Corpus Estimates
```{r calc_pos_entropy}
get_entropies <- function(role, sen_length, utterances) {

  if(role == "Target_Child") {
    sub_utterances <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(stem, " ") + 1) # uses stems of words, not original words
  } else {
     sub_utterances <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(stem, " ") + 1)
  }

  # 
  # 
  # ggplot(adult_utterances, aes(x = length)) +
  #   geom_histogram(fill = "white", color = "black")

  tokens <- sub_utterances %>%
    filter(length == sen_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(word_order, word)

  tokens %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(role = role, length = sen_length)
}

@@

new_utterances <- prov_utterances %>% filter(speaker_role=="Target_Child") %>% mutate(len = str_count(stem, " ") + 1)
#toks <- new_utterances %>%

ggplot(new_utterances, aes(x=len)) +
  geom_histogram(binwidth = 1)
```

compute estimates
```{r calc_pos_entropy}
#get counts of each word in each position of utterances of length sen_length
#from the collection of CHILDES utterances in utterances with speaker_role in role
get_counts <- function(role, sen_length, utterances) {

  if(role == "Target_Child") {
    sub_utterances <- utterances %>%
      filter(speaker_role == "Target_Child") %>%
      mutate(length = str_count(stem, " ") + 1) # uses stems of words, not original words
  } else {
     sub_utterances <- utterances %>%
      filter(speaker_role != "Target_Child") %>%
      mutate(length = str_count(stem, " ") + 1)
  }

  sub_utterances %>%
    filter(length == sen_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, stem) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n())
}

#compute the unigram entropy measure from the counts of each word in each position
unigram_entropy <- function(counts) {

  counts %>%
    group_by(word_order, word) %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(role = role, length = sen_length)
}

@@

entropies <- map(2, ~ get_counts("not child", .x, prov_utterances) %>%
                   bind_rows %>%
                   unigram_entropy) %>%
  bind_rows()

new_utterances <- prov_utterances %>% filter(speaker_role=="Target_Child") %>% mutate(len = str_count(stem, " ") + 1)
#toks <- new_utterances %>%

ggplot(new_utterances, aes(x=len)) +
  geom_histogram(binwidth = 1)
```

English Conditional Entropy
```{r conditional_entropy}
#compute all Conditional Entropy from all one-way pairs of word positions
all_conditional_entropy <- function(df) {
  max_len <- max(df$word_order)
  #combs <- combn(1:max_len, 2, simplify = F)
  perms <- permutations(max_len, 2, 1:max_len, repeats.allowed = F) 
  combs <-  setNames(split(perms, seq(nrow(perms))), rownames(perms))

@@

#perform the actual Conditional Entropy calculation
conditional_entropy <- function(df, X, Y) { #Y is conditioning variable

@@

ce <- map(counts, all_conditional_entropy)

@@

ggplot(ce_br, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable")

@@

N-Gram frequencies (saved for later)
```{r ngram_frequencies}
m_prov <- prov_utterances %>%
          filter(speaker_role == "Target_Child") %>%
          mutate(length = str_count(stem, " ") + 1) %>% 
          filter(length >= 2)

b_prov <- m_prov %>% mutate(bigrams = paste(unlist(textcnt(stem, n = 2, split = " ", method = "string")), collapse = ",")) #get all the counts of bigrams from all of the dataframe
counts <- b_prov$bigrams[1] %>% strsplit(split=',') %>% unlist() %>% as.numeric()
fileConn <- file("counts.txt")
writeLines(b_prov$bigrams[1], fileConn)
close(fileConn)

b_prov <- m_prov %>% mutate(bigrams = paste(unlist(names(textcnt(stem, n = 2, split = " ", method = "string"))), collapse = ",")) #get all of the bigrams from the entire dataframe
bigrams <- b_prov$bigrams[1] %>% strsplit(split=',') %>% unlist()
fileConn <- file("bigram_words.txt")
writeLines(b_prov$bigrams[1], fileConn)
close(fileConn)

>>>>

@@

#compute the unigram entropy measure from the counts of each word in each position
unigram_entropy <- function(tokens) {

  tokens %>%
    group_by(word_order, word) %>%
    summarise(n = n()) %>%
    tidyboot(summary_function = function(x) x %>% 
               summarise(entropy = entropy(n, unit = "log2")),
             statistics_functions = function(x) x %>%
             summarise_at(vars(entropy), funs(ci_upper, ci_lower))) %>%
    mutate(role = role, length = sen_length)
}

@@

  rbind(start_slopes, second_slopes, mid_slopes, penult_slopes, end_slopes)
}
```

Compute Providence Corpus Estimates
```{r calc_pos_entropy}
tokens <- extract_stem_tokens("not child", 6, 30, prov_utterances)

@@

@@

English Mutual Information
```{r mutual_information}

@@

English Conditional Entropy
```{r conditional_entropy}
#compute all Conditional Entropy from all one-way pairs of word positions
all_pairwise_ce <- function(df) {
  max_len <- max(df$word_order)

  perms <- permutations(max_len, 2, 1:max_len, repeats.allowed = F) 
  combs <-  setNames(split(perms, seq(nrow(perms))), rownames(perms))

@@

#perform the actual Conditional Entropy calculation
get_ce <- function(df, X, Y) { #Y is conditioning variable

@@

ce <- map(counts, all_conditional_entropy) %>% bind_rows()

@@

ggplot(ce, aes(x = X, y = ce, color = as.factor(Y))) + 
  facet_wrap(~ length) + 
  geom_point() + 
  geom_line() + 
  ggtitle("Conditional entropy vs. conditioned random variable")

@@

### 2018-10-29 ldp/LDP_entropy.Rmd
Reorganized files, deleted redundant and obsfucating code

---
title: Non-English Conditional Entropy and Mutual Information
author: Joe Klafka
date: "`r Sys.date()`"
output: 
  html_document:
    toc: false
    number_sections: false
    theme: lumen
    toc_float: false
    code_folding: show 
---

>>>>

---
title: Non-English Conditional Entropy and Mutual Information
author: Josef Klafka
date: "`r Sys.date()`"
output: 
  html_document:
    toc: false
    number_sections: false
    theme: lumen
    toc_float: false
    code_folding: show 
---

### 2018-10-29 wiki_entropy/wiki_entropy.Rmd
Reorganized files, deleted redundant and obsfucating code

---
title: Wikipedia Text Mining and Entropy Analysis
author: Josef Klafka and Dan Yurovsky
date:
output: 
  html_document:
    toc: false
    number_sections: false
    theme: lumen
    toc_float: false
    code_folding: show 
---

@@

system(paste("python3 wiki_entropy.py", LANGUAGE, sep = " "))
```

```{r slope_analysis, include=FALSE, eval = F}
df <- read_csv("~/Documents/Labwork/Joe/Positional-Information/wiki_entropy/ru_df.csv")

@@

wiki_tokens %>%
    filter(word_order %in% c(1, 2)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2"), n = sum(n)) %>%
    spread(word_order, entropy) %>%
    group_by(length) %>%
    mutate(diff = `2` - `1`) %>%
  ggplot(aes(x = length, y = diff)) +
  geom_point(aes(size = n)) +
  geom_smooth(se = F) +
  scale_x_log10() #log length stats

@@

  tokens <- df %>%
    filter(length == sen_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, sentence) %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(word_order, word) %>%
    filter(word_order <= length)

@@

```{r slope_stuff, include = F, eval = F}

xmf_df <- read_csv("xmf_df.csv")

#get_slopes("not child", 6, py$xmf_df, "gloss")

gtx <- extract_wiki_tokens(6, 1000, xmf_df)

gtx %>%
    filter(word_order %in% c(1,2)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2"), n = sum(n)) %>%
    spread(word_order, entropy) %>%
    group_by(length) %>%
    mutate(diff = `2` - `1`) %>%
  ggplot(aes(x = length, y = diff)) +
  geom_point(aes(size = n)) +
  geom_smooth(se = F) +
  scale_x_log10() #log length stats

get_wiki_slopes(min_length = 6, max_length = 50, utterances=xmf_df)

```{r garbage}
# extract_stem_tokens <- function(role, min_length, utterances) {
#   
#   REPS <- 100
#   
#   if (role == "child") {
#     lengths <- utterances %>%
#       filter(speaker_role == "Target_Child") %>%
#       mutate(length = str_count(stem, " ") + 1)
# 
#   } else {
#     lengths <- utterances %>%
#       filter(speaker_role != "Target_Child") %>%
#       mutate(length = str_count(stem, " ") + 1)
#   }
#   
#   tokens <- lengths %>% 
#     filter(length >= min_length) %>%
#     mutate(utterance_id = 1:n()) %>%
#     unnest_tokens(word, stem) %>%
#     group_by(utterance_id) %>%
#     mutate(word_order = 1:n()) %>%
#     group_by(length, word_order, word) %>%
#     summarise(n = n()) 
# }
#get_slopes("not child", 6, py$xmf_df, "gloss")

# sub_tokens <- xmf_df %>% 
#      mutate(gloss = str_trim(gloss)) %>%
#      mutate(length = str_count(gloss, " +") +1) %>%
#      filter(length >= min_length) %>%
#      filter(length <= max_length) %>%
#      mutate(utterance_id = 1:n())
# 
# 
# sub_tokens %>%
#      unnest_tokens(word, gloss, token = stringr::str_split, pattern = " +") %>%
#      group_by(utterance_id) %>%
#      mutate(word_order = 1:n()) %>%
#      group_by(utterance_id) %>%
#      summarise(n = n()) %>%
#      filter(n != 6) %>%
#      left_join(sub_tokens) %>%
#      select(gloss, n, length) %>%
#      View()

#entropies <- map(6:12, ~get_entropies(.x, py$xmf_df)) %>%
#  bind_rows()

#ggplot(entropies, aes(x = word_order, y = empirical_entropy,
#                      ymin = ci_lower, ymax = ci_upper)) +
#  facet_wrap(~ length) + 
#  geom_pointrange() +
#  geom_smooth(se = F)

# extract_stem_tokens <- function(role, min_length, utterances) {
#   
#   if (role == "child") {
#     lengths <- utterances %>%
#       filter(speaker_role == "Target_Child") %>%
#       mutate(length = str_count(stem, " ") + 1)
# 
# } else {
#     lengths <- utterances %>%
#       filter(speaker_role != "Target_Child") %>%
#       mutate(length = str_count(stem, " ") + 1)
# }
#   
#   tokens <- lengths %>% 
#     filter(length >= min_length) %>%
#     mutate(utterance_id = 1:n()) %>%
#     unnest_tokens(word, stem) %>%
#     group_by(utterance_id) %>%
#     mutate(word_order = 1:n()) %>%
#     group_by(length, word_order, word) %>%
#     summarise(n = n()) 
# }
# 
# extract_gloss_tokens <- function(role, min_length, utterances) {
#   
#   if (role == "child") {
#     lengths <- utterances %>%
#       filter(speaker_role == "Target_Child") %>%
#       mutate(length = str_count(gloss, " ") + 1)
# 
# } else {
#     lengths <- utterances %>%
#       filter(speaker_role != "Target_Child") %>%
#       mutate(length = str_count(gloss, " ") + 1)
# }
#   
#   tokens <- lengths %>% 
#     filter(length >= min_length) %>%
#     mutate(utterance_id = 1:n()) %>%
#     unnest_tokens(word, gloss) %>%
#     group_by(utterance_id) %>%
#     mutate(word_order = 1:n()) %>%
#     group_by(length, word_order, word) %>%
#     filter(word_order <= length) %>% 
#     summarise(n = n()) 
# }
```

>>>>

---
title: Wikipedia Text Mining and Entropy Analysis
author: Josef Klafka and Dan Yurovsky
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: false
    number_sections: false
    theme: lumen
    toc_float: false
    code_folding: show 
---

@@

system(paste("python3 get_wiki_df.py", LANGUAGE, sep = " "))
```

```{r slope_analysis, include=FALSE, eval = F}
df <- read_csv("wiki_df.csv")

@@

# plot the entropy slope for sentences of length min_length to max_length
wiki_tokens %>%
    filter(word_order %in% c(1, 2)) %>%
    group_by(length, word_order) %>%
    summarise(entropy = entropy(n, unit = "log2"), n = sum(n)) %>%
    spread(word_order, entropy) %>%
    group_by(length) %>%
    mutate(diff = `2` - `1`) %>%
  ggplot(aes(x = length, y = diff)) +
  geom_point(aes(size = n)) +
  geom_smooth(se = F) +
  scale_x_log10() #log length stats

@@

  tokens <- utterances %>% 
    mutate(gloss = str_trim(gloss)) %>%
    mutate(length = str_count(gloss, pattern = " +") + 1) %>% 
    filter(length >= min_length) %>%
    filter(length <= max_length) %>%
    mutate(utterance_id = 1:n()) %>%
    unnest_tokens(word, gloss, token = stringr::str_split, pattern = " +") %>%
    group_by(utterance_id) %>%
    mutate(word_order = 1:n()) %>%
    group_by(length, word_order, word) %>%
    summarise(n = n())

@@
